Topological Equivariant Artist Model

### 2022-01-26 slides/main.tex
fiber bundle def fix

\usepackage{tabulary}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}

@@

        \column{0.39\textwidth}

@@

                  \onslide*<2-6|handout:1-2>{\dfiberc}

@@

                  \onslide*<3-6|handout:1-2>{\dtotalc} 

@@

                   \onslide*<1-6|handout:1-2>{\dbasec}

@@

     \column{0.59\textwidth}

@@

        \begin{description}
            \item<1-5|handout:1>[\textcolor{base}{Base Space}]{$( \dbasec, \mathcal{T})$, $\dbasepointc \in \opensetc \subset \dbasec$}
            \item<2-5|handout:1>[\textcolor{fiber}{Fiber Space}]{$\dfiberc\restriction_{\dbasepointc} = \pi^{-1}(\dbasepointc)$}
            \item<3-5|handout:1>[\textcolor{total}{Total Space}]{ $\dtotalc\restriction_{\opensetc} = \dbasec\restriction_{\opensetc} \times \dfiberc\restriction_{\opensetc}$ \\ for all $\opensetc \subset K$}
        \end{description}}

@@

        \begin{description}
            \item[\textcolor{base}{Continuity Type \dbasec}]{how data elements are organized (topological properties) \cite{wilkinsonGrammarGraphics2005,munznerWhatDataAbstraction2014})}
            \item[\textcolor{fiber}{Fields Type \dfiberc}] {generalization of a schema - named and typed date fields \cite{spivakSIMPLICIALDATABASES, spivakDatabasesAreCategories2010}}
            \item[\textcolor{total}{Data Type \dtotalc}]{continuity type + field type}

@@

            \begin{description}
                \item[\textcolor{base}{Continuity Type \gbasec}]{how pixels are organized in the display space}
                \item[\textcolor{fiber}{Display Type \gfiberc}] {display specifications}
                \item[\textcolor{total}{Graphic Type \gtotalc}]{continuity type + display type}

@@

    \only<5|handout:1>{
        \begin{alertblock}{Sections}
            \begin{align*}         
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}
        \end{align*}

@@

    \begin{alertblock}{Data \cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992}}
        \begin{align*}
        \dsectionc(\dbasepointc) = &\delementc,\; \dbasepointc\in \opensetc\subset \dbasec,\; \delement \in \dfiberc\restriction_{\dbasepointc}\\
        &\delementc=\{field_0:value, \cdots field_i:value, \cdots field_n:value\}
        \end{align*}

@@

        \begin{alertblock}{Graphic}
            \begin{align*}         
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \coloneqq \big\{\gsectionc: \opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} \; \bigm{\vert} \pi(\gsectionc(\gbasepointc)) = \gbasepointc\;for\, all\; \gbasepointc \in \opensetgc \big\}\\
            \vspace{5pt}\\
            \gsectionc(\gbasepointc) = d,\; \gbasepointc\in \opensetgc\subset \gbasec,\; d \in \dfiberc\restriction_{\gbasepointc}\\
            for\;example:\; d=\{x,\,y,\,r,\,g,\,b\}
            \end{align*}

@@

\begin{frame}{$\dfuncc = (\dfunchc, \dfuncpullc, \dfunctc)$}
    \begin{tikzcd}[ampersand replacement = \&]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
        \arrow[rr, "\dfuncpullc", color=action] 
        \&  \& 
        \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} 
        \arrow[rr, "\dfunctc", color=action] 
        \&  \& 
        \cgamma{\opensetc^{\prime}}{\dfunctc\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} \\
        \&  \&  
        \&  \& \\
        \opensetc 
        \arrow[uu, "{\sheafc_{\dbasec, \dtotalc}}", maps to, color=sheaf]                 
        \&  \& 
        \opensetc^{\prime} 
        \arrow[ll, "\dfunchc", color=action] 
        \arrow[uu, "{\dfuncpullc\sheafc_{\dbasec, \dtotalc}}"', maps to, color=sheaf] 
        \arrow[rruu, "{\dfunctc\dfuncpullc\sheafc_{\dbasec, \dtotalc}}"', maps to, color=sheaf] 
        \&  \& 
    \end{tikzcd}
    \begin{itemize}
        \item Base $\dbasec$ Type stays same: $\dfunchc: \dbasec \rightarrow \dbasec$
        \item Fiber $\dfiberc$ Type stays the same: $\dfunctc: \dfiberc \rightarrow \dfiberc$
        \item Section Transform: $\dfuncc: \dsectionc^{a}\restriction_{\opensetc} \mapsto \dsectionc^{b}\restriction_{\opensetc^{\prime}}$
    \end{itemize}
\end{frame}

\begin{frame}{\dfunctc}
    $\dfunctc$ applies a monoid action $\monoidc$ on a fiber set $\dfiberc$
    \begin{equation*}
        \dfunctc: \monoidc \times \dfiberc \rightarrow \dfiberc
    \end{equation*}
    meaning that, by definition of a monoid, the following properties are satisfied
    \begin{description}
        \item[identity]: $\dfunctc(\textcolor{monoid}{e}, \delementc) = \delementc, \delementc \in \dfiberc, \textcolor{monoid}{e} \in \monoidc$
        \item[associativity]  $\dfunctc(\textcolor{monoid}{g}, \dfunctc(\textcolor{monoid}{h}, \delementc)) = \dfunctc(\textcolor{monoid}{g}\circ \textcolor{monoid}{h}, \delementc), \textcolor{monoid}{g}, \textcolor{monoid}{h} \in \monoidc, \delementc \in \dfiberc$
    \end{description}
\begin{block}{Multivariate?} 
    \label{def:category:F} The fiber category $\mathcal{\dfiberc}$ is a monoidal category\cite{milewskiCategoryTheoryProgrammers}, which means it is a category equipped with a bifunctur $\otimes: \mathcal{\dfiber} \times \mathcal{\dfiber} \rightarrow \mathcal{\dfiber}$
    \begin{itemize}
      \item \textit{object} set \dfiberc with actions \monoidc \cite{nlab:monoid}.
      \item \textit{morphisms} $\dfiberc \otimes \dfiberc \rightarrow \dfiberc$, $\monoidc \otimes \monoidc \rightarrow \monoidc$ and unit
    \end{itemize}
\end{block}
\end{frame}

\begin{frame}{Continuity Equivariance: $\dfunchc_{\gbasec}\circ \vindexc = \vindexc \circ \dfunchc_{\dbasec}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
        \opensetgc 
        \arrow[rr, "\vindexc", color=functor] 
        \arrow[dd, "\dfunchc_{\gbasec}"', dashed, color=action] 
        \&  \& 
        \opensetc 
        \arrow[dd, "\dfunchc_{\dbasec}", color=action] \\
        \&  \& \\
        \opensetgc^{\prime} 
        \arrow[rr, "\vindexc"', color=functor]
        \&  \& 
        \opensetc^{\prime}\\
        \underbrace{\dbasec \times {[0,1]}^{m}}_{\gbasec} \arrow[rr,"\vindex", maps to, color=functor] \& \& \dbasec
        \end{tikzcd}
    \end{equation*}

@@

    \begin{proposition}{}
        \begin{align*}
            \vartistc(\dsectionc^{a}) = \vartistc(\dsectionc^{b}) &\centernot\implies \dsectionc^a = \dsectionc^b \\
            \vartistc(\dsectionc^{a})  = \vartistc(\dsectionc^{b}) &\implies \vartistc(\dfuncc_{\dsectionc}(\dsectionc^{a})) = \vartistc(\dfuncc_{\dsectionc}(\dsectionc^{b})) \
        \end{align*}
    \end{proposition}

@@

\begin{frame}
    dummy sheet
\end{frame}

\begin{comment}
\subsection{Contributions}
\begin{frame}{Contributions}
    \begin{description}
        \item[Topological] continuity  
        \item[Equivariant] monoid action 
        \item[Artist] Matplotlib $\textit{artist}: \textit{data} \rightarrow \textit{graphic}$ 
        \item [Model] 
    \end{description}
\end{frame}

\section{Math}

\begin{frame}{Topological Equivariant Artist Model}
    \centering
    An artist $\mathscr{\vartist}$ is an equivariant map 
    \begingroup 
    \Huge
    \begin{equation*}
        \mathscr{\vartist}: \mathscr{\dtotal} \rightarrow \mathscr{\gtotal}
    \end{equation*}
    \endgroup
    from data $\mathscr{\dtotal}$ space to graphic $\mathscr{\gtotal}$ space. 
\end{frame}

\subsection{Data}
\begin{frame}{Model data as a fiber bundle \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}}
    A fiber bundle is a tuple $(\dtotal,\,\dbase,\,\pi ,\,\dfiber)$ defined by the map $\pi$
    \begin{equation*}
        \label{eq:fiber_bundle}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiber \arrow[r, hook] \& \dtotal \arrow[r, "\pi"] \& \dbase
        \end{tikzcd}
    \end{equation*}
    \begin{description}
        \pause
        \item[total space \dtotal] topology
        \pause
        \item[fiber space \dfiber] schema
        \pause
        \item[base space \dbase] continuity
    \end{description}
\end{frame}

\begin{frame}{Encode variable types in a schema like fiber \cite{spivakDatabasesAreCategories2010,spivakSIMPLICIALDATABASES}}
    \begin{figure}[H]
        \centering
        \includegraphics[width=\textwidth]{figures/math/fiber.png}
    \label{fig:data_fiber_example}
    \end{figure}
\end{frame}

\begin{frame}{Monoids are the structure of the components of \dfiber}
    \begin{figure}[H]
        \centering
        \includegraphics[height=.3\textheight]{figures/math/fiber.png}
    \label{fig:data_fiber_example}
    \end{figure}
        \begin{equation*}
            \dfiber = \dfiber_0 \times \ldots \times \dfiber_i \times \ldots \times \dfiber_n
        \end{equation*}
        \pause
        Monoid actions $\monoid_{i}$ (e.g. rotation, partial ordering) define the structure on $\dfiber_i$
        \begin{equation*}
            \bullet: \monoid_i\times \dfiber_i \rightarrow \dfiber_i
        \end{equation*}
        where $\bullet$ is associative and has an identity action. 
\end{frame}

\begin{frame}{\dbase\ is an indexing space}
    \begin{figure}[H]
        \includegraphics[width=1\textwidth]{figures/math/base.png}
    \label{fig:base_example}
    \end{figure}
\end{frame}

\begin{frame}{Data are sections \dsection\ on \dtotal}
    For any fiber bundle, there exists a map
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiber \arrow[r, hook] \& \dtotal \arrow[d, "\pi"'] \\
                              \& \dbase \arrow[u, "\dsection"', bend right]
        \end{tikzcd}
    \end{equation*}
     s.t. $\pi(\dsection(\dbasepoint)) = \dbasepoint$. $\Gamma(\dtotal)$ is the set of all global sections.
     \begin{figure}[H]
        \includegraphics[width=1\linewidth]{figures/math/fiberbundle.png}
        \label{fig:data_sections}
    \end{figure}
\end{frame}

\subsection{Graphic}
\begin{frame}{Graphic Bundle $(\gtotal,\,\gbase,\,\pi ,\,\gfiber)$} % watch dr explaination
    \only<2->{Continuity is preserved via the many \gbasepoint\ to one \dbasepoint\ map $\vindex: \gbase\rightarrow\dbase$}

    \only<1>{
        \begin{equation*} 
            \begin{tikzcd}[ampersand replacement=\&]
                F \arrow[r, hook] \& E \arrow[d, "\pi"']              \& D \arrow[r, hook] \& H \arrow[d, "\pi"']              \\
                                  \& K \arrow[u, "\tau"', bend right] \&                   \& S \arrow[u, "\rho"', bend right]
                \end{tikzcd}
            \end{equation*}}
    \only<2->{
    \begin{equation*} 
        \begin{tikzcd}[ampersand replacement=\&]
            F \arrow[r, hook] \& E \arrow[d, "\pi"']              \& D \arrow[r, hook] \& H \arrow[d, "\pi"']                                 \\
                              \& K \arrow[u, "\tau"', bend right] \&                   \& S \arrow[ll, "\xi"'] \arrow[u, "\rho"', bend right]
            \end{tikzcd}
        \end{equation*}}
    \only<3->{   
    \gfiber\ is a proxy for the target display, for example $(x,\, y,\, r,\, g,\, b) \in \gfiber$}
    \pause
    \begin{figure}[H] %%%bring up one at a time
        \begin{overprint}
            \onslide<4|handout:0>\includegraphics[width=1\linewidth]{figures/math/scatter_s.png}
            \onslide<5|handout:0>\includegraphics[width=1\linewidth]{figures/math/line_s.png}
            \onslide<6>\includegraphics[width=1\linewidth]{figures/math/image_s.png}
        \end{overprint}
    \end{figure}
\end{frame}

\subsection{Artist}
\begin{frame}{Visual bundle $(\vtotal,\,\dbase,\,\pi ,\,\vfiber)$}
    \begin{equation*}
        \mathcal{A}:\mathcal{E}\rightarrow\mathcal{H}
    \end{equation*}
\pause
\begin{equation*}
    \label{eq:artist_diagram}
    \begin{tikzcd}[ampersand replacement=\&]
        \dtotal^{\prime} \arrow[r, "\vchannel"] \arrow[rd, "\pi"'] \& \vtotal \arrow[d, "\pi"] \& \vindex^*\vtotal \arrow[r, "\vmark"] \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"'] \& \gtotal \arrow[ld, "\pi"] \\
                                              \& \dbase                  \& \gbase \arrow[l, "\vindex"']                                              \&                    
        \end{tikzcd}
\end{equation*}
\pause
\begin{equation*}
    \vartist: \mathcal{O}(\dtotal) \rightarrow \mathcal{O}(\gtotal)
\end{equation*}
\end{frame}

\begin{frame}{Visualization Assembly Function}
    \begin{figure}
        \includegraphics[width=\textwidth]{figures/math/path_of_q.png}
    \end{figure}
    \pause
    \begin{equation*}
        \label{eq:nu_expanded}
        \{\vchannel_{0}, \ldots, \vchannel_{n}\}: \{\dsection_{0}, \ldots, \dsection_{n}\} \mapsto \{\vsection_{0}, \ldots, \vsection_{n}\}
    \end{equation*}
    \pause
    \begin{equation*}
        Q = \nu \circ \tau
    \end{equation*}
\end{frame}

\begin{frame}{Group Equivariance: Stevens' Scales \cite{stevensTheoryScalesMeasurement1946}}
\begin{table}[H]
    \begin{tabularx}{\textwidth}{|l|l|X|}\toprule
        \textbf{scale} & \textbf{group} & \textbf{constraint} \\\midrule
        nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
        ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
        interval &  translation &  $\vchannel (x + c) = \vchannel(x) + c$ \\
        ratio &  scaling &  $\vchannel(xc) = \vchannel(x)*c $\\ \bottomrule
    \end{tabularx}
\end{table}
\end{frame}

\begin{frame}{Monoid Equivariance: Partial Orders}
    \begin{figure} 
        \begin{overprint}
            \onslide<1|handout:0>\includegraphics[width=1\linewidth]{figures/math/partial.png}
            \onslide<2|handout:0>\includegraphics[width=1\linewidth]{figures/math/partial_invalid.png}
            \onslide<3>\includegraphics[width=1\linewidth]{figures/math/partial_fixed.png}
        \end{overprint}
    \end{figure}
\end{frame}

\begin{frame}{Visualization Equivariance}
    \begin{figure}[H]
        \includegraphics[width=\textwidth]{figures/math/diff_type_q.png}
    \end{figure}
    \begin{equation*}
        \vmark(\vsection) = \vmark(\vsection^{\prime})\implies \vmark(m\circ\vsection) = \vmark(m\circ\vsection^{\prime})
    \end{equation*}

@@

\begin{frame}{Scatter: $\vmark(xpos, ypos)(\alpha, \beta)$}
    \begin{figure}[H]
        \begin{overprint}
            \onslide<1|handout:0>\includegraphics[width=1\linewidth]{figures/math/scatter_q.png}
            \onslide<2|handout:0>\includegraphics[width=1\linewidth]{figures/math/scatter_with_s.png}
        \end{overprint}
    \end{figure}   
\end{frame}

>>>>

\usepackage{tabulary}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}

@@

        \column{0.31\textwidth}

@@

              \onslide*<3-6|handout:1-2>{\dfiberc}

@@

              \onslide*<1-6|handout:1-2>{\dtotalc} 

@@

               \onslide*<2-6|handout:1-2>{\dbasec}

@@

     \column{0.69\textwidth}

@@

        \begin{description}[style=nextline]
            \item<1-5|handout:1>[\textcolor{total}{Total Space}]{$(\dtotalc, \mathcal{T}_{\dtotalc})$}
            \item<2-5|handout:1>[\textcolor{base}{Base Space}]{$(\dbasec, \mathcal{T}_{\dbasec}),\; \dbasepointc \in \opensetc \subseteq \dbasec$}
            \item<3-5|handout:1>[\textcolor{fiber}{Fiber Space}]{$\dfiberc\restriction_{\dbasepointc} = \pi^{-1}(\dbasepointc), \dfiberc = \dfiberc\restriction_{\dbasepointc}\; \forall \dbasepointc \in \dbasec$}

@@

        \begin{description}[style=nextline]
            \item[\textcolor{total}{Data \dtotalc}]{continuity + fields}
            \item[\textcolor{base}{Continuity \dbasec}]{how data elements are organized (topological properties) \cite{wilkinsonGrammarGraphics2005}, index (key) space \cite{munznerWhatDataAbstraction2014})}
            \item[\textcolor{fiber}{Fields \dfiberc}] {generalization of a schema - named and typed date fields \cite{spivakSIMPLICIALDATABASES, spivakDatabasesAreCategories2010}}

@@

            \begin{description}[style=nextline]
                \item[\textcolor{total}{Graphic \gtotalc}]{virtual rendered output}
                \item[\textcolor{base}{Continuity \gbasec}]{topology of graphic in rendered space}
                \item[\textcolor{fiber}{Display \gfiberc}] {generalization of renderer specifications, e.g. \{xy,rgba\}, \{xy, cymk\}, \{xyz, rgba\}}

@@

    \only<4-5|handout:1>{
        \begin{alertblock}{}
            \begin{description}[style=nextline]
                \item[\textcolor{section}{Sections}]{$\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}$}
                \item[Locally Trivial] {for every point $\dbasepointc \in \dbasec$, there exists an open neighborhood $\dbasepointc \in \opensetc \subseteq \dbasec$ s.t. there is a homeomorphism $\pi^{-1}(\opensetc)\xrightarrow{\varphi} \opensetc \times \dfiberc$}
                \item[(Globally) Trivial]{$\dtotalc = \dbasec \times \dfiberc$}

@@

    \begin{alertblock}{}
        \begin{description}[style=nextline]
            \item[\textcolor{section}{Data} \cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992}]{$
        \dsectionc(\dbasepointc) = \;\delementc,\; \dbasepointc\in \opensetc \subseteq \dbasec,\; \delementc \in \dfiberc\restriction_{\dbasepointc}$} 
        \item[]{$\delementc=\{field_0:value, \cdots field_i:value, \cdots field_n:value\}$}

@@

        \begin{alertblock}{}
            \begin{description}[style=nextline]
                \item[\textcolor{section}{Graphic}]{$\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \coloneqq \big\{\gsectionc: \opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} \; \bigm{\vert} \pi(\gsectionc(\gbasepointc)) = \gbasepointc\;for\, all\; \gbasepointc \in \opensetgc \big\}$}
                \item[] {$\gsectionc(\gbasepointc) = \gelementc,\; \gbasepointc\in \opensetgc\subseteq \gbasec,\; \gelementc \in \dfiberc\restriction_{\gbasepointc}$}
                \item[] $\gelementc=\{x,\,y,\,r,\,g,\,b\}$

        \end{description}    
    \end{alertblock}
    }
\end{frame}

@@

\begin{frame}{What is \dfuncc?}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc$ 
        \end{description}
    \end{block}

    \begin{block}{fiber transform equivariance}
        The fiber $\dfiberc$ is the sole object of an arbitrary category $\mathcal{C}$. The bundle morphisms 
        \begin{equation*}
            \dfuncc \in Hom(\dfiberc,\dfiberc)
        \end{equation*} 
        are the set of morphisms that also preserve fiber structure.
    \end{block}
\end{frame}

\begin{frame}{$\dfuncc = (\dfunchc, \dfuncpullc, \dfunctc)$}
    \begin{tikzcd}[ampersand replacement = \&]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
        \arrow[rr, "\dfuncpullc", color=action] 
        \&  \& 
        \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} 
        \arrow[rr, "\dfunctc", color=action] 
        \&  \& 
        \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} \\
        \&  \&  
        \&  \& \\
        \opensetc 
        \arrow[uu, "{\sheafc_{\dbasec, \dtotalc}}", maps to, color=sheaf]                 
        \&  \& 
        \opensetc^{\prime} 
        \arrow[ll, "\dfunchc", color=action] 
        \arrow[uu, "{\dfuncpullc\sheafc_{\dbasec, \dtotalc}}"', maps to, color=sheaf] 
        \arrow[rruu, "{\dfuncpullc\sheafc_{\dbasec, \dtotalc}}"', maps to, color=sheaf] 
        \&  \& 
    \end{tikzcd}
    \begin{itemize}
        \item Base $\dbasec$ Type stays same: $\dfunchc: \dbasec \rightarrow \dbasec$
        \item Fiber $\dfiberc$ Type stays the same: $\dfunctc: \dfuncpullc \dtotalc \rightarrow \dfuncpullc\dtotalc$ s.t. $\pi(\dfuncpullc\dtotalc) = \pi(\dfunctc(\dfuncpullc\dtotalc))$ 
        \item Section Transform: $\dfuncc: \dsectionc^{a}\restriction_{\opensetc} \mapsto \dsectionc^{b}\restriction_{\opensetc^{\prime}}$
    \end{itemize}
\end{frame}

\begin{frame}{Continuity Equivariance: $\dfunchc_{\dbasec}\circ \vindexc = \vindexc \circ \dfunchc_{\gbasec}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
        \opensetgc 
        \arrow[rr, "\vindexc", color=functor] 
        \arrow[dd, "\dfunchc_{\gbasec}"', dashed, color=action] 
        \&  \& 
        \opensetc 
        \arrow[dd, "\dfunchc_{\dbasec}", color=action] \\
        \&  \& \\
        \opensetgc^{\prime} 
        \arrow[rr, "\vindexc"', color=functor]
        \&  \& 
        \opensetc^{\prime}\\
        \underbrace{\dbasec \times {[0,1]}^{m}}_{\gbasec} \arrow[rr,"\vindex", maps to, color=functor] \& \& \dbasec
        \end{tikzcd}
    \end{equation*}

@@

    \begin{proposition}{}
        \begin{align*}
            \vartistc(\dsectionc^{a}) = \vartistc(\dsectionc^{b}) &\centernot\implies \dsectionc^a = \dsectionc^b \\
            \vartistc(\dsectionc^{a})  = \vartistc(\dsectionc^{b}) &\implies \vartistc(\dfuncc_{\dsectionc}(\dsectionc^{a})) = \vartistc(\dfuncc_{\dsectionc}(\dsectionc^{b})) \
        \end{align*}
    \end{proposition}
\end{frame}

\begin{frame}{Multiple Fields: $\dfuncc = (\dfunchc, \dfuncpullc, \prod\limits_{i=0}^{n}\dfunctc_i)$} 
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, column sep=2ex]
                \dfunctc_0 \circ \dfuncpullc \dtotalc_0 
                \arrow[rdd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_i \circ \dfuncpullc \dtotalc_i 
                \arrow[dd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_n \circ \dfuncpullc \dtotalc_n 
                \arrow[ldd, "\pi" description] \& = \& 
                \prod\limits_{i=0}^{n} 
                \dfunctc_i \circ \dfuncpullc \dtotalc 
                \arrow[dd, "\pi" description] \\    
                \&\&\&\&\\    
                \& 
                {(\dfunchc=\dfunchc_{i \in [0,n]}) \circ \dbasec }                                             \& \& = \& 
                \dfunchc \circ \dbasec                                                        
                \end{tikzcd}                                              
    \end{equation*}

    \begin{block}{Add New Field to E}
        \begin{description}[style=newline]
            \item[construct] {$\odot:\dfiberc_{field} \times \dbasec \rightarrow \dtotalc_{field}$}
            \item[concatenate]{$\otimes: \dtotalc_{field} \times \dtotalc \mapsto \dtotalc$ s.t. $\pi(\dtotalc_{field}) = \pi(\dtotalc)$}
        \end{description}
    \end{block}

@@

\begin{frame}{Field Equivariance}

    \begin{equation*}
        \oslash: \vartistc \times \dfiberc \rightarrow visual\; encoding
    \end{equation*}

\begin{equation*}
    \begin{tikzcd}[ampersand replacement = \&]
            \& 
            {\sheafc_{\dbasec, \dtotalc}}
            \arrow[rr, "\vartistc"]                   
            \&  \& 
            \sheafc_{\vartist} 
            \arrow[rd, "\oslash_{\dfiber_{field}}"]           \&                        \\
            \dfiberc_{field} 
            \arrow[ru, "\otimes_{\dtotalc} \circ \odot_{\dbasec}"] 
            \arrow[rd, "\otimes_{\dtotalc^{\prime}} \circ \odot_{\dbasec^{\prime}}"'] 
            \& \& \& \& 
            visual\;encoding \\
            \& 
            {\sheafc_{\dbasec^{\prime}, \dtotalc^{\prime}}} 
            \arrow[rr, "\vartistc"'] 
            \& \& 
            \sheafc_{\vartist}^{\prime} 
            \arrow[ru, "\oslash_{\dfiber_{field}}"'] 
            \&                       
    \end{tikzcd}
\end{equation*}

@@

\section{Construction}
\begin{frame}{What's in the $\vartist$ black box?}
    \note{Add box around figure & lable it artist}
    \begin{figure}
        \includegraphics[width=1\textwidth]{../paper/figures/path_of_q.png}
    \end{figure}
\end{frame}

\begin{frame}{Encoding + Assembly Stages}
    %E-V and Q diagram    
\end{frame}
\begin{frame}{Encoding + Assembly}
    \begin{figure}
        \includegraphics{../paper/figures/q_hat.p}
    \end{figure}
\end{frame}
\begin{frame}{Domain and Range}
    \begin{figure}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[.5\textwidth]{../paper/figures/fiberbundle.png}
        \end{subfigure}
        \begin{subfigure}{.5\textwidth}
            \includegraphics[.5\textwidth]{../paper/figures/render.png}
        \end{subfigure}
    \end{figure}
\end{frame}

\begin{frame}{Example $\dfunctc$: Stevens' Scales \cite{stevensTheoryScalesMeasurement1946}}
\begin{table}[H]
    \begin{tabularx}{\textwidth}{|l|l|X|}\toprule
        \textbf{scale} & \textbf{group} & \textbf{constraint} \\\midrule
        nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
        ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
        interval &  translation &  $\vchannel (x + c) = \vchannel(x) + c$ \\
        ratio &  scaling &  $\vchannel(xc) = \vchannel(x)*c $\\ \bottomrule
    \end{tabularx}
\end{table}
\end{frame}

\begin{comment}
\begin{frame}{Scatter: $\vmark(xpos, ypos)(\alpha, \beta)$}
    \begin{figure}[H]
        \begin{overprint}
            \onslide<1|handout:0>\includegraphics[width=1\linewidth]{figures/math/scatter_q.png}
            \onslide<2|handout:0>\includegraphics[width=1\linewidth]{figures/math/scatter_with_s.png}
        \end{overprint}
    \end{figure}   
\end{frame}
